Structured Versus Decorated Cospans

### 2020-11-26 cospans.tex
fixed Definition A.10 - monoidal double category

\begin{defn}
\label{defn:monoidal_double_category}
A \define{monoidal double category} is a pseudomonoid in $\Dbl$. Explicitly, it is a double category equipped with double functors $\otimes \maps \lD \times \lD \to \lD$ and $I \maps 1 \to \lD$ where $1$ is the terminal double category, along with invertible transformations called the \define{associator}:
\[  \alpha \maps \otimes \, \circ \; (1_{\lD} \times \otimes ) \Rightarrow \otimes \; \circ \; (\otimes \times 1_{\lD}) ,\]
\define{left unitor}:
\[ \ell \maps \otimes \, \circ \; (1_{\lD} \times I) \Rightarrow 1_{\lD} ,\]
and \define{right unitor}:
\[ r \maps \otimes \,\circ\; (I \times 1_{\lD}) \Rightarrow 1_{\lD} \]
satisfying the pentagon and triangle identities.
\end{defn}

>>>>

\begin{defn}
\label{defn:monoidal_double_category}
A \define{monoidal double category} is a pseudomonoid in $\Dbl$. 
\end{defn}

This definition neatly packages a large quantity of information.   When we unpack it, we see a monoidal double category is a double category $\lD$ with:
\begin{itemize}
\item monoidal structures on both $\lD_0$
and $\lD_1$, each with tensor product $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, obeying the pentagon and triangle identities,
\item the structure of a double functor on $\otimes$:
that is, invertible globular 2-morphisms
\[ \chi \maps (M_1\otimes N_1)\odot (M_2\otimes N_2) \xrightarrow{\sim}
(M_1\odot M_2)\otimes (N_1\odot N_2)\]
\[ \mu \maps U_{A\otimes B} \xrightarrow{\sim} (U_A \otimes U_B)\]
\end{itemize}
These structures must obey a number of equations, which can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC}.
